---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anabass

The goal of anabass is to analyse basic structure of sentences for better writeings.

anabass is from a name of fish ginus anabas. 
anabas was is thought to climb tree, but not in actual. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("matutosi/anabass")
```

<!--
You can also install from CRAN:
```{r, eval = FALSE}
install.packages("anabass")
```
 -->


## Example

You can use `fun()` to analyse basic structure.

```{r example}
library(anabass)
library(dplyr)
library(ggplot2)

devtools::load_all(".")
library(moranajp)
review_sentences <- 
  review_chamame |>
  unescape_utf() |>
  add_sentence_no() |>
  clean_up() |>
  dplyr::filter(chap == 5) |>
  dplyr::select(sentence, word = "\u539f\u5f62") |>
  dplyr::filter(word != "") |>
  dplyr::group_by(sentence) |>
  dplyr::summarise(word = reduce(word, paste, sep = ";")) |>
  `$`(_, "word") |>
  stringr::str_split(";")

df <- connect_sentences(review_sentences)

df |>
  ggplot2::ggplot(ggplot2::aes(x = x_start, y = sentence, label = word)) +
  ggplot2::geom_point() +
  gghighlight::gghighlight(highlight == TRUE, label_key = word) +
  ggplot2::scale_y_reverse() +
  ggplot2::theme_bw()

df <- 
  review_chamame |>
  unescape_utf() |>
  dplyr::filter(chap == 5) |>
  add_sentence_no() |>
  dplyr::distinct(sect, para, sentence) |> 
  dplyr::right_join(df)

df |>
  ggplot2::ggplot(ggplot2::aes(x = x_start, y = sentence, label = word)) +
  ggplot2::geom_text() +
  ggplot2::scale_y_reverse() +
  ggplot2::theme_bw() + 
  ggplot2::facet_wrap(vars(para))


```

## Citation

Toshikazu Matsumura (2024) anabass: Analyse Basic Structure of Sentences for Better Writing. https://github.com/matutosi/anabass/.
